Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-02 lloveras_2020_Albert.tex

\albert{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show \albert{latitude-longitude} maps of DEMT results for both \albert{rotations. Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels (\albert{see} Section \ref{demt}). Thick-black \albert{curves indicate} the magnetic open/closed \albert{boundaries} based on the magnetic field of \albert{the} AWSoM model.

\albert{Target} CR-2082 was highly axisymmetric \albert{(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$. \albert{Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$. \albert{In both rotations the open/closed} boundaries derived from the respective AWSoM model \albert{very accurately} match the shape of \albert{contour levels} of the tomographic maps of both the \albert{electron density and temperature. The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}

\albert{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208. \albert{In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase. A similar behabiour is seen in CR-2208, belonmging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious. This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.

@@

{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. \albert{As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}

@@

\albert{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in grey color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} \albert{Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III. On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}

\albert{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24. Here, we verify the existence of this type of structuire for the two target rotations. The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate of course the CHs.}

\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\emph{Top panels:} \albert{latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

\albert{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs. \albert{For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively. The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas? (yo especifiqué ``medianas". Son efectivamente tan iguales?}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

\albert{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types. From top to bottom \albert{results are shown for} type 0 to type III \albert{field lines}. From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ \albert{(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ \albert{and} $\aTm$, \albert{with the median value $m$ indicated in each plot}.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{ (by Albert) The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.} }
\label{histos_fulldemt}
\end{center}
\end{figure}

For all type of lines, Table \ref{tabla_demt} \albert{summarizes a} quantitative comparative analysis between the results of the two \albert{target rotations}. For CR-2082 quantities are expressed as absoulte values, \albert{while} for CR-2208 they are informed \albert{as a precentual variation} relative to the corresponding results for CR-2082. The following major results concerning the structure of each rotation individually and their comparison can be drawn.

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value. \albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Doy dos ejemplos para no dejar dudas. Para $\NCB$ de Type-II: $1.0\,(-21\%)$. Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
\label{tabla_demt}
\end{table}

%\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
\albert{Throughout} the equatorial streamer of both rotations, \albert{type 0, I and II legs, which are associated to progressively} increasing latitudes, \albert{progressively exhibit} decreasing {coronal base} density, \albert{increasing density scale height, and increasing electron temperature}. In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of \albert{those observed for the type 0 lines in the core of} the equatorial streamer. \notebyalbert{No estoy seguro de entender y acordar con la siguiente frase.} \emph{Histograms with sharp populations indicates that for both rotations the values of all physical quantities exhibit a strong symmetry between both hemispheres.}

\notebyalbert{A continuación modifiqué la sintaxis en que esto se explica (creo que para mejor), y puse números acordes a los de la Tabla-1, los que estaban no eran consistentes con ella.} \albert{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}

@@

\notebyalbert{Cambié este párrafo.} \albert{To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$. In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities \albert{$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively. \notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq. 11, 12, y 10. Sugiero que en los histogramas listes los $\phi$ y sus medianas de arriba a abajo en este orden, ya que igual los deberás re-hacer para poner la letra griega $\phi$ (y otros cambios requeridos).}

@@

\albert{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations. Also, in the range of sensitivity of the AUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}

\albert{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$. As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}

>>>>

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights of interest were selected here, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic results ($1.025\,\mrsun$), one of the lowest heights where the AWSoM results are consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the magnetic open/closed {boundaries} based on the magnetic field of {the} AWSoM model.

{Target} CR-2082 was highly axisymmetric {(i.e, a high azymuthal symmetry)} and showed two ARs (active region) in latitude $+30\mdeg$ and longitude $50\mdeg$ and $120\mdeg$. {Target CR-2208 was much less axisymmetric and it} showed two AR, one around latitude $+5\mdeg$ and longitude $140\mdeg$ and the other around latitude-longitud $+5\mdeg$, $300\mdeg$. {In both rotations the open/closed} boundaries derived from the respective AWSoM model {very accurately} match the shape of {contour levels} of the tomographic maps of both the {electron density and temperature. The magneticlly open regions of the AWSoM model are those associated to CHs, and the magnetically closed ones to the equatorial streamer belt.}

{Visual inspection of Figures \ref{momento1} and \ref{momento2} indicates} that the streamer belt region of CR-2082 was denser and colder than CR-2208. {In the case of CR-2082, which belongs to the deep minimum epoch between SC2 24/25, the temperature in the equatorial latitudes tends to decrease with height while in the mid-latitudes tends to increase. A similar behaviour is seen in CR-2208, belonging to the declining phase of SC25, but being a much less axisymmetric target this behaviour is not so obvious. This structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.} Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.

@@

{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in grey color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, violet and green color, respectively.} {Of the 45000 legs selected for CR-2082, 14\% are type 0, 38\% are type I, 23\% are type II and 25\% type III. On the other hand, of the 59000 legs selected for CR-2208, 8\% are type 0, 43\% are type I, 22\% are type II and 30\% type III.}

{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the SC 24/25 solar minimum by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed how equatorial down loops in streamers were also to be found in the deep minimum between SCs 23/24. Here, we verify the existence of this type of structure for the two target rotations. The relatively smaller population of down loops seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate of course the CHs.}

%\notebyalbert{No comprendo esta frase:} \emph{This classification of types of lines automatically leads to specific regions arranged along all longitudes associated with different thermodynamic, with good symmetry between both hemispheres in both rotations.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR2082 (left) and CR2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs (see text) are shown in blue, red, violet and green color, respectively.} \notebyalbert{ (by Albert) The violet color is not distinguishable from the blue one really, they gonna claim this so you better change it now. How about ORANGE? You can try a light-shade of orange, something that VERY clearly contrasts with the RED. Also, ORANGE is better suited, as these type-II loops are also of class UP (while violet suggests DOWN). Use then the same color for Figure 5.}}
\label{rpoint_demt}
\end{center}
\end{figure}

{Figure \ref{gradt_demt} shows frequency histograms (normalized to the total amount of selected field lines ) of the temperature radial gradient ($\dr\Tm$) for legs of type 0, I, II and III.} The lack of population around values close to zero is due to the requirement $|\rho_t| > 0.5$ which discards quasi-isothermal legs. {For both rotations, the median value of $\dr\Tm$ is very similar for each type of leg, being  $\approx -2.5$, $2.3$ and $2.4\,\MK/\mrsun$ for legs of type 0, I and II, respectively. The only notable difference between both rotations is the characteristic value $\dr\Tm\approx 4.5\,\MK/\mrsun$ for legs of type III for CR-2208, which is about half that for CR-2082.} \notebyalbert{Estos vaores que informas son medianas o modas? (yo especifiqué ``medianas". Son efectivamente tan iguales?}\diego{si, las medianas tienen esos valores.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for the different {four types of legs} shown in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel). \notebyalbert{This Figure is still stretched in LaTeX, i.e. you are forcing the height and the width. Do not do that. Set only the width.}}
\label{gradt_demt}
\end{center}
\end{figure}

{Figure \ref{histos_fulldemt} shows} the statistical results of both rotations for all field lines types. From top to bottom {results are shown for} type 0 to type III {field lines}. From left to right the panels show the statistical distribution of $\NCB \equiv \sqravgN(r=1.055)$ {(the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{{Statistical distribution of DEMT results traced along legs of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR-2082 and CR-2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.}}
\label{histos_fulldemt}
\end{center}
\end{figure}

For all type of lines, Table \ref{tabla_demt} {summarizes a} quantitative comparative analysis between the results of the two {target rotations}. For CR-2082 quantities are expressed as absoulte values, {while} for CR-2208 they are informed {as a precentual variation} relative to the corresponding results for CR-2082. The following major results concerning the structure of each rotation individually and their comparison can be drawn.

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value. \notebyalbert{ (by Albert) Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Doy dos ejemplos para no dejar dudas. Para $\NCB$ de Type-II: $1.0\,(-21\%)$. Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
\label{tabla_demt}
\end{table}

%\noindent\diego{Si queda una asociacion directa entre los tipos de lineas y las estructuras de streamer, CH etc entonces usaria esos nombres a continuacion.}\\
{Throughout} the equatorial streamer of both rotations, {type 0, I and II legs, which are associated to progressively} increasing latitudes, {progressively exhibit} decreasing {coronal base} density, {increasing density scale height, and increasing electron temperature}. In both rotations the CH regions are characterized sub-MK temperatures, and coronal base densities of order $\approx 1/2$ of {those observed for the type 0 lines in the core of} the equatorial streamer.

{A comparison of the results between the two rotations shows that compared to CR-2082, target rotation CR-2208 was characterized by $\approx 15-20\%$ lower values of the electron density at the coronal base, $\approx 10-30\%$ larger values of density scale height, and $\approx 15-25\%$ larger values of the electron temperature.}

@@

\notebyalbert{Cambié este párrafo.} {To analyze the loop-integrated energy flux quantities, we selected closed loops where both legs meet the requirements of Section \ref{trace}, and both posses the same sign of the radial gradient of the electron temperature $\dr\Tm$. In this way, according to the clasification of both its legs, each given loop was classified as of type 0 (small down loop), I (small up loop), or II (large up loop).}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{{Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) Very nice, but it needs slightly larger fonts, they are very tiny. You should work out all histograms at the same time and understand what is going on. TITLE here is PERFECT, but  XYOUTS and LABELS here are SLIGHTLY small. One comment, did you use "!Dp!N", where p=r,c,h, for the XYOUTS? Or did you use a "subscript" command. If the latter, then try !D instead.}}
\label{energia_demt}
\end{center}
\end{figure}

For both target rotations, and for loops of type 0, I and II, Figure \ref{energia_demt} shows the frequency histogram of the loop-integrated energy flux quantities {$\phi_r$, $\phi_c$ and $\phi_h$ in blue, green and red color}, respectively. \notebyalbert{Notá que puse las cosas en el orden que las cosas se calculan: Eq. 11, 12, y 10. Sugiero que en los histogramas listes los $\phi$ y sus medianas de arriba a abajo en este orden, ya que igual los deberás re-hacer para poner la letra griega $\phi$ (y otros cambios requeridos).}

@@

{For both rotations, the value of the integrated radiative power $E_r$, measured by the quantity $\phi_r$, progressively decreaces for loops of type 0, I and II. This is due to $E_r\propto N_e^2\,\Lambda(T_e)$, with both factors cooperating to maximize $E_r$ for loops of type 0 and minimize it for loops of type II. As shown in Figure \ref{histos_fulldemt} and Table \ref{tabla_demt}, loops of type 0, I and II are characterised by progressively decreasing electron density for both rotations. Also, in the range of sensitivity of the EUVI and AIA instruments, namely 0.5–3.0 MK \citep{nuevo_2015}, the radiative loss function $\Lambda(T)$ has a local maximum at $\Tc\approx 1\,\MK$. According to Figure \ref{histos_fulldemt}, loops of type 0, I and II are characterised by progressively larger electron temperature, and progressively farther from the value $\Tc$, for both rotations.}

{In the case of the quantity $\phi_c$, its sign depends on that of the conductive flux $F_c$. As shown in \citet{maccormack_2017}, down loops (type 0) and up loops (type I and II) are characterized by $\phi_c<0$ and $\phi_c>0$, respectively, which is verified in Figure \ref{energia_demt}.}
